R dyntrace report

### 2018-01-31 graphs/report.Rmd
A lot of changes to report wrt visualizing old data.

---
title: "R dyntrace report"
author: "K. Siek, A. Goel"
output: 
  html_document:
    theme: flatly # default cerulean journal flatly readable spacelab united cosmo lumen paper sandstone simplex yeti
    highlight: tango
params:
  CSV_DIR: "/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/"
  PRINT_DATA: TRUE
---

@@

@@

pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
load_local_csv <- function (csv_file) {
    path <- file.path(params$CSV_DIR, csv_file)
    write(paste("reading", path), stderr())
    as_tibble(read.csv(path))
}
print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
                                      ifelse(x < 1000000, 
                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""), 
                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "mln", sep=""))))
pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)

make_graphs_for_packages <- function(data, f) {
  graphs <- lapply((data %>% select(name) %>% distinct %>% pull(name)), f(data))
  do.call("grid.arrange", c(graphs, ncol=ceiling(sqrt(length(graphs)))))
}

@@

missing_basic_info <- 
  basic_info %>% summarise(
    name="...",
    datasets="...",
    n.datasets="...",
    n.functions="...",
    n.calls="...",
    n.promises="...",
    n.promise.forces="...",
    n.promise.lookups="...", 
    n.alien.promises="...",
    n.alien.promise.forces="..."
  )
```

## Dataset

@@

<!--r path -->
## Overview

@@

## Promise accesses

@@

@@

## Number of accesses to a promise

### Aggregate

@@

### Distribution per package

@@

### Separate results per package

``` {r, "number of accesses to a promise, separate per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
make_graphs_for_packages(load_local_csv("promise_evaluations.csv"), function(data) function(package) {
  evaluations <- 
    data %>% 
    filter(name == !!package) %>%
    mutate(percent=100*number/sum(number)) %>%
    mutate(labels=no.of.evaluations) %>%
    mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
    mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
                                    max(no.of.evaluations, na.rm=TRUE)+1, 
                                    no.of.evaluations))

@@

  ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
    geom_col() +
    scale_x_discrete(limit=0:11, labels=c(0:10,">10")) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(), 
          axis.ticks.y=element_blank(),
          axis.text.x=element_text(angle = 90, size = 5, vjust=.5),
          legend.position="none") +
    xlab(package)
})
```

## Promise code types

### Aggregate

@@

### Separate results per package

``` {r, "promise code types, separate per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
available_sexps <- promise_types %>% select(type) %>% distinct %>% pull(type)

make_graphs_for_packages(promise_types, function(data) function(package) {
  promise_types <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(type) %>% summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

@@

  ggplot(promise_types, aes(x=type, y=number)) + 
    geom_col() +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(), 
          axis.ticks.y=element_blank(),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          legend.position="none") +
    xlab(package)
})
```

## What's inside promises?

```{r, "what's inside promises", echo=FALSE, fig.width=10, fig.height=4.5}
promise_full_types <-
  load_local_csv("promise_full_types.csv") %>%
  group_by(type) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number)) %>% 
  mutate(type=as.character(type)) %>%
  filter(grepl("^PROM", type)) %>%
  mutate(type=gsub("PROM", "", type))
  #mutate(type=ifelse(len(type) > 15, paste0(strtrim(type, 13), ".."), type))

ggplot(promise_full_types, aes(x=type, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank(), 
        legend.position="none", 
        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
  ylab("No. of promises") + 
  xlab("Promise full type (PROM)")
```

<div style="font-size: 50%">
Promise types follow the type designations in ``Rinternals.h``.  
<!--**α→β** indicates that type **α** variously evaluates to type **β**.  -->
**α** indicates that the promise contains the expression of type **α**.  
**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
<!--**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
</div>

## What do promises return?

``` {r, "what do promises return",  echo=FALSE, fig.width=10, fig.height=5}
return_types <- 
  load_local_csv("return_types.csv") %>%
  group_by(type) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(return_types, aes(x=type, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank(), 
        legend.position="none", 
        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
  ylab("No. of promises") + 
  xlab("Return type")
```

@@

@@

```{r, "what do specific promises return", echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
types_to_return_types <- 
  load_local_csv("promise_code_to_return_types.csv") %>%
  group_by(types) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

@@

## Promise forces by types

### Aggregate

@@

### Distribution per package

<!--``` {r, "promise forces by types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
make_graphs_for_range(force.histogram.by.type, "type", max.col=5, f=function(data)
  ggplot(data, aes(x=no.of.forces, y=percent)) +
    geom_violin(draw_quantiles = c(.25, .5, .75)) +
    scale_y_continuous(labels=pp_perc) +
    theme(axis.title.x=element_blank(), 
          axis.title.y=element_blank(), 
          legend.position="none")
)
```-->

## Promise evaluation distances

<!--Effective distance is the distance from the call where a promise originated to the call in which it was evaluated. It is measured along the call graph (along inbound edges).  Since the data is gathered from a trace, the call graph is a tree.-->
<!--
```{r, "promise forces by types, separate per package", echo=FALSE, fig.width=10, fig.height=4.5}
actual_distances <- 
  load_local_csv("actual_distances.csv") %>%
  group_by(actual_distance) %>% 
  summarise(number=sum(number, na.rm = TRUE)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(actual_distances, aes(x=actual_distance, y=number)) + 
  geom_col() +
  scale_x_discrete(limits=c(NA,0:20,">20",-1)) +
  scale_y_continuous(labels=pp_trunc) +
  ylab("No. of promises") + 
  theme(axis.title.x=element_blank())
```
-->

@@

## Functions and calls by type

<center>
<div class="col2">
<div class="together">
```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
calls.types <- 
  load_local_csv("call_types.csv") %>%
  group_by(type) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

slices <- (calls.types %>% arrange(number))$number
labels <- (calls.types %>% arrange(number) %>% mutate(type = ifelse(percent>1, paste0(as.character(type), " (", floor(percent), "%)", sep=""), "")))$type
par(mar=c(0,2,2,2))

pie(slices, labels, main="Call types")
```
</div>

```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
function.types <- 
  load_local_csv("function_types.csv") %>%
  group_by(type) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

slices <- (function.types %>% arrange(number))$number
labels <- (function.types %>% arrange(number) %>% mutate(type = ifelse(percent>1, paste0(as.character(type), " (", floor(percent), "%)", sep=""), "")))$type
par(mar=c(0,2,2,2))

pie(slices, labels, main="Function types")
```
</div>
</center>

@@

## Byte-code compilation

<center>
<div class="col2">
<div class="together">
```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
closure.call.compilation.histogram <- 
  load_local_csv("compiled_calls.csv") %>%
  group_by(compiled) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

slices <- (closure.call.compilation.histogram)$number
labels <- (closure.call.compilation.histogram)$compiled %>% as.character
par(mar=c(0,2,2,2))

pie(slices, labels, main="Compiled closures (calls)")
```
</div>

@@

## Interactions among promises

>>>>

---
title: "R dyntrace report"
author: "K. Siek, A. Goel"
output: 
  html_document:
    theme: flatly # default cerulean journal flatly readable 
                  # spacelab united cosmo lumen paper sandstone simplex yeti
    highlight: tango
    toc: true
    toc_depth: 3
    number_sections: true
params:
  CSV_DIR: "/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/"
  PRINT_DATA: TRUE
---

@@

knitr::opts_chunk$set(cache=TRUE)

@@

pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
load_local_csv <- function (csv_file) {
    path <- file.path(params$CSV_DIR, csv_file)
    write(paste("reading", path), stderr())
    as_tibble(read.csv(path, stringsAsFactors=FALSE))
}
print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
                                      ifelse(x < 1000000, 
                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""), 
                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""))))
pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)

#http://mathematicalcoffee.blogspot.cz/2014/06/ggpie-pie-graphs-in-ggplot2.html
ggpie <- function (dat, by, totals, labels=by) {
    ggplot(dat, aes_string(x=factor(1), y=totals, fill=by)) +
        geom_bar(stat='identity', color='black') +
        guides(fill=guide_legend(override.aes=list(colour=NA))) + # removes black borders from legend
        coord_polar(theta='y') +
        theme(axis.ticks=element_blank(),
            axis.text.y=element_blank(),
            axis.text.x=element_text(colour='black'),
            axis.title=element_blank(),
            legend.position='none') +
    scale_y_continuous(breaks=cumsum(dat[[totals]]) - dat[[totals]] / 2, labels=dat[[labels]])
}

make_graphs_for_packages <- function(data, f, max.col=10) {
  graphs <- lapply((data %>% select(name) %>% distinct %>% pull(name)), f(data))
  do.call("grid.arrange", c(graphs, ncol=min(max.col, ceiling(sqrt(length(graphs))))))
}

@@

missing_basic_info <- 
  basic_info %>% summarise(
    name="...",
    datasets="...",
    n.datasets="...",
    n.functions="...",
    n.calls="...",
    n.promises="...",
    n.promise.forces="...",
    n.promise.lookups="...", 
    n.alien.promises="...",
    n.alien.promise.forces="..."
  )

 n.packages <- basic_info %>% count %>% pull(n)

 # some graphical stuff
 package_figure_width <- 10
 package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
 package_figure_rows <- ceiling(n.packages/package_figure_columns)
 package_figure_height <- ceiling(10/7 * package_figure_rows)
```

# Dataset

@@

<!--r path -->
# Overview

@@

# Promise accesses

@@

## Distribution per package

@@

# Number of accesses to a promise

## Aggregate

@@

## Distribution per package/vignette

@@

## Separate results per package/vignette

``` {r, "number of accesses to a promise, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
make_graphs_for_packages(load_local_csv("promise_evaluations.csv"), max.col=package_figure_columns, f=function(data) function(package) {
  evaluations <- 
    data %>% 
    filter(name == !!package) %>%
    mutate(percent=100*number/sum(number)) %>%
    mutate(labels=no.of.evaluations) %>%
    mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
    mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
                                    max(no.of.evaluations, na.rm=TRUE)+1, 
                                    no.of.evaluations))

@@

  ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
    geom_col() +
    scale_x_discrete(limit=0:11, labels=c(0:10,">10")) +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(evaluations, number)))) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.ticks.y=element_blank(),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

# Promise code types

## Aggregate

@@

## Separate results per package/vignette

``` {r, "promise code types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
available_sexps <- promise_types %>% select(type) %>% distinct %>% pull(type)

make_graphs_for_packages(promise_types, max.col=package_figure_columns, f=function(data) function(package) {
  promise_types <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(type) %>% summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

@@

  ggplot(promise_types, aes(x=type, y=number)) + 
    geom_col() +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(promise_types, number)))) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.ticks.y=element_blank(),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

# Type traces

```{r, "what's inside promises", echo=FALSE, fig.width=10, fig.height=4.5}
promise_full_types <-
  load_local_csv("promise_full_types.csv") %>%
  group_by(type) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number)) %>% 
  mutate(type=as.character(type)) #%>%
  #filter(grepl("^PROM", type)) %>%
  #mutate(type=gsub("PROM", "", type))
  #mutate(type=ifelse(len(type) > 15, paste0(strtrim(type, 13), ".."), type))

promise_full_types %>% 
  arrange(desc(number)) %>%
  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
  kable(col.names=c("type trace", "number", "percent"), align="lrr")
```

<div style="font-size: 50%">
Promise types follow the type designations in ``Rinternals.h``.  
<!--**α→β** indicates that type **α** variously evaluates to type **β**.  -->
**α** indicates that the promise contains the expression of type **α**.  
**PROM→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.  
**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.    
**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  
**...** is a type that could not has not been correctly determined.
</div>

# Promise return types

## Aggregate

``` {r, "promise return types, aggregate",  echo=FALSE, fig.width=10, fig.height=5}
return_types <- 
  load_local_csv("return_types.csv")

ggplot(return_types %>%   
         group_by(type) %>% 
         summarise(number=sum(number)) %>% 
         mutate(percent=100*number/sum(number)), 
       aes(x=type, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank(), 
        legend.position="none", 
        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
  ylab("No. of promises") + 
  xlab("Return type")
```

@@

## Distribution per package/vignette

``` {r, "promise return types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
make_graphs_for_range(return_types, "type", max.col=5, f=function(data)
  ggplot(data, aes(x=type, y=percent)) +
    geom_violin(draw_quantiles = c(.25, .5, .75)) +
    scale_y_continuous(labels=pp_perc) +
    theme(axis.title.x=element_blank(), 
          axis.title.y=element_blank(), 
          legend.position="none")
)
```

## Separate results per package/vignette

``` {r, "promise return types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
available_sexps <- return_types %>% select(type) %>% distinct %>% pull(type)

make_graphs_for_packages(return_types, max.col=package_figure_columns, f=function(data) function(package) {
  promise_types <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(type) %>% summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  ggplot(promise_types, aes(x=type, y=number)) + 
    geom_col() +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(promise_types, number)))) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.ticks.y=element_blank(),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

@@

```{r, "what do specific promises return", echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
types_to_return_types <- 
  load_local_csv("promise_code_to_return_types.csv") %>%
  group_by(types) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number)) %>%
  arrange(desc(number))

@@

# Promise forces by types

## Aggregate

@@

## Distribution per package

```{r, "promise forces by types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}

types <- force.histogram.by.type %>% pull(type) %>% unique
forces <- force.histogram.by.type %>% pull(no.of.forces) %>% unique
featured_packages <- force.histogram.by.type %>% pull(name) %>% unique

force_histogram_filled_in <- 
  expand.grid(type=types, no.of.forces=forces, name=featured_packages) %>%
  left_join(force.histogram.by.type, by=c("type", "no.of.forces", "name")) %>%
  mutate(number=ifelse(is.na(number), 0, number),
         percent=ifelse(is.na(percent_overall), 0, percent_overall)) %>%
  mutate(forces=paste0(type, "/", no.of.forces)) %>%
  #select(forces, number, percent, name) %>% 
  arrange(forces) %>% 
  as_tibble

make_graphs_for_range(force_histogram_filled_in, "forces", max.col=5,
  f=function(data) 
    ggplot(data, aes(x=forces, y=percent)) +
    geom_violin() +
    #geom_violin(draw_quantiles=c(.25, .5, .75)) + # this one errors out and idk why
    scale_y_continuous(labels=pp_perc) +
    theme(axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          legend.position="none")
)
```

## Separate results per package/vignette

``` {r, "promise forces by types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
#type_range <- force_histogram_filled_in %>% select(type) %>% distinct %>% pull(forces)

make_graphs_for_packages(force_histogram_filled_in, max.col=package_figure_columns, f=function(data) function(package) {
  force_histogram <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(type, no.of.forces) %>% 
      summarise(number=sum(number)) %>% 
      mutate(percent=100*number/sum(number))
    #group_by(type) %>% summarise(number=sum(number)) %>% 
    #mutate(percent=100*number/sum(number))

  ggplot(
    force_histogram,
    aes(x=type, y=number, fill=factor(no.of.forces))) + 
    geom_bar(stat="identity", position="dodge") +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(force_histogram, number)))) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.ticks.y=element_blank(),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

# Promise evaluation distances

## Aggregate

<!--Effective distance is the distance from the call where a promise originated to the call in which it was evaluated. It is measured along the call graph (along inbound edges).  Since the data is gathered from a trace, the call graph is a tree.-->

```{r, "promise actual distances, aggregate", echo=FALSE, fig.width=10, fig.height=4.5}
actual_distances <- load_local_csv("actual_distances.csv")

ggplot(actual_distances %>% 
         group_by(actual_distance) %>% 
         summarise(number=sum(number, na.rm=TRUE)) %>% 
         mutate(percent=100*number/sum(number)), aes(x=actual_distance, y=number)) + 
  geom_col() +
  scale_x_discrete(limits=c(NA,0:20,">20",-1)) +
  scale_y_continuous(labels=pp_trunc) +
  ylab("No. of promises") + 
  theme(axis.title.x=element_blank())
```

@@

## Distribution per package/vignette

``` {r, "promise actual distances, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
make_graphs_for_range(actual_distances %>%
  mutate(actual_distance = ifelse(is.na(actual_distance), "NA", actual_distance)),
  "actual_distance", max.col=5, f=function(data)
  ggplot(data, aes(x=actual_distance, y=percent)) + 
  geom_violin() +
  scale_y_continuous(labels=pp_perc) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="none")
)
```

# Calls and functions by type

## Aggregate

<center>
<div class="col2">
<div class="together">
```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
calls_types <- load_local_csv("call_types.csv")

data <- 
  calls_types %>% 
  group_by(type) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(data, aes(x=type, y=number)) + 
  geom_bar(stat="identity") +
  ylab("No. of calls") + 
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank())
```
</div>

```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
function_types <- load_local_csv("function_types.csv") #FIXME use the concatenated data

data <- function_types %>%
  group_by(type) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(data, aes(x=type, y=number)) + 
  geom_bar(stat="identity") +
  ylab("No. of function definitions") + 
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank())
```
</div>
</center>

@@

## Calls by type, distribution per package/vignette

``` {r, "calls by type, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
make_graphs_for_range(calls_types %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
  "type", max.col=5, f=function(data)
  ggplot(data, aes(x=type, y=percent)) + 
  geom_violin() +
  scale_y_continuous(labels=pp_perc) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="none")
)
```

## Functions by type, distribution per package/vignette

``` {r, "functions by type, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
make_graphs_for_range(function_types %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
  "type", max.col=5, f=function(data)
  ggplot(data, aes(x=type, y=percent)) + 
  geom_violin() +
  scale_y_continuous(labels=pp_perc) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="none")
)
```

## Calls by type, separate results per package/vignette

``` {r, "calls by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
make_graphs_for_packages(calls_types, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(type) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  ggplot(package_data, aes(x=type, y=number)) + 
    geom_bar(stat="identity") +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
    theme(axis.title.y=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

## Functions by type, separate results per package/vignette

``` {r, "functions by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
make_graphs_for_packages(function_types, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(type) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  ggplot(package_data, aes(x=type, y=number)) + 
    geom_bar(stat="identity") +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
    theme(axis.title.y=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

# Byte-code compilation

<center>
<div class="col2">
<div class="together">
```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
closure_call.compilation.histogram <- load_local_csv("compiled_calls.csv") # compiled

```
</div>

@@

# Interactions among promises
